\newpage
\begin{center}
{\bf ACKNOWLEDGEMENTS}
\end{center}

First and foremost, I would like to thank my advisor Gil Paz for all the support and guidance during the last six years. His advice was instrumental in advancing my career as a physicist, and I am eternally indebted to that. I want to thank my collaborators Alexey Petrov and Cody Grant, for their contribution to this work. Also, I would like to thank the members of my committee Alexey Petrov, Sean Gavin, Abhijit Majumder and Mark Baskaran, for reviewing my work and providing constructive feedback. I want to convey my gratitude to Ratna Naik and David Cinabro for their roles as Chair of the Department. Without their excellent leadership, this work would not be possible.\par 
I want to thank my parents Kanishka Gunawardana and Pushpa Herath, for their unconditional support and encouragement to achieve my goals. I would also like to thank my in-laws for their constant support and guidance. Special thank goes to my sister Malsrini Malarachchi without her help I would not be here.\par  
I acknowledge all my friends at Wayne State University and the University of Kelaniya for making my life more enjoyable. I specially thank Navoda Thushari for being such a great mentor and friend. Her enthusiastic teaching was pivotal to my scientific career.\par  
Last but not least, I thank my wife, Nirasha Perera, who has always been there with me during all the ups and downs in my life. My journey would not have been possible without her sacrifices and endurance.


